% Cover letter template — compile with XeLaTeX or pdfLaTeX
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{fontspec}
\setmainfont{TeX Gyre Heros}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

\textbf{Norah Mohammed Alkabkabi}\\
Makkah, Saudi Arabia \textbar{} +966\,541\,539\,940 \textbar{}
\href{mailto:nora.alkabkabi@gmail.com}{nora.alkabkabi@gmail.com}

\vspace{12pt}
\today

\vspace{12pt}
Hiring Manager\\
\textit{[Company Name]}\\
\textit{[City, Saudi Arabia]}

Dear Hiring Manager,

I am writing to apply for the \textit{[Position Title]} role at \textit{[Company Name]}. I recently completed my Bachelor of Science in Software Engineering at Umm Al-Qura University with a GPA of \textbf{3.67/4.00} and second honors, and I am eager to contribute practical development and quality-assurance skills gained through cooperative training and my graduation project.

During my four-month cooperative training at King Abdulaziz Hospital in Mecca, I developed and deployed two full-stack internal systems using Node.js, Express, and MySQL. I built more than 17 digital HR forms with automated approval workflows, implemented 67 automated tests, and deployed solutions on the hospital's production server. This experience strengthened my ability to deliver reliable software in a structured, mission-critical environment.

For my graduation project, \textbf{Ruwad}, I contributed to a live student-clubs platform (\href{https://ruwad.space}{ruwad.space}) built with Laravel, Svelte, and Inertia.js. My work included SRS-aligned Pest testing, bilingual PDF reporting, and CI/CD automation via GitHub Actions. I am particularly interested in roles where software quality, clear documentation, and collaborative delivery matter---including software engineering, QA engineering, and technical instruction.

I would welcome the opportunity to discuss how my academic foundation, hands-on project work, and commitment to quality can support your team. Thank you for your time and consideration.

Sincerely,\\[18pt]
Norah Mohammed Alkabkabi

\end{document}
